Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-14 icse/paper.tex
stuff

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

In this study, we define a technique to detect clones such that they can be refactored. We propose a tool to detect such clones and automatically refactor a subset of them. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On basis of these results, we decide which clones improve system design and thus should be refactored. We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.

@@

\section{Background}
This study researches an intersection of code clone and refactoring research.

\subsection{Code clone terminology}
Clone class collection, clone class, clone instance, cloned node, token.

\subsection{Code clone definitions}
Quick overview of clone type definitions

@@

\subsection{Allowing variability in a controlled set of expressions}
%Explain type 2, why it is not always refactorable, solution
Often, fragments in source code do not match exactly. Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose. To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{color}
\usepackage{listings}
\usepackage{parcolumns}

\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
\definecolor{pred}{rgb}{0.9,0,0}
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}

\lstset{language=Java,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=true,
  commentstyle=\color{pgreen},
  keywordstyle=\color{pblue},
  numbers = left,
  stringstyle=\color{pred},
  basicstyle=\ttfamily,
  moredelim=[il][\textcolor{pgrey}]{$$},
  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
}

\definecolor{lightyellow}{HTML}{fffdcc}
\definecolor{doublelightyellow}{HTML}{fffa9c}
\definecolor{lightgreen}{HTML}{dcffd4}
\definecolor{lightblue}{HTML}{e0ffff}
\definecolor{lightred}{HTML}{ffe0e0}
\definecolor{lightpink}{HTML}{ffe0ff}
\definecolor{lightorange}{HTML}{ffede0}
\definecolor{lightpurple}{HTML}{f0e0ff}
\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightGreen}{\makebox[0pt][l]{\color{lightgreen}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{lightblue}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightRed}{\makebox[0pt][l]{\color{lightred}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightPink}{\makebox[0pt][l]{\color{lightpink}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightOrange}{\makebox[0pt][l]{\color{lightorange}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{lightpurple}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}

\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

In this study, we define clones that can be refactored. We propose a tool to detect such clones and automatically refactor a subset of them. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On basis of these results, we decide which clones improve system design and thus should be refactored. %We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.

@@

\section{Background}
This study researches an intersection of code clone and refactoring research. In this background section, we will explain the required background knowledge for terms used throughout this study.

\subsection{Code clone terminology}
In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
\textbf{Clone instance}: A single cloned fragment.
\textbf{Clone class}: A set of similar clone instances.

%\subsection{Code clone definitions} Optional -> may do this if it adds something to the story
%Quick overview of clone type definitions

@@

\subsection{Allowing variability in a controlled set of expressions}
%Explain type 2, why it is not always refactorable, solution
Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}. Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose. To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.

We define the following expressions as refactorable when varied:
\begin{itemize}
  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
  \item \textbf{Method references}: Only if the return value of referenced method match (or are not used).
\end{itemize}
Often when allowing such variance, tradeoffs come into play. For instance, variance in literals may require the introduction of a parameter, increasing the required effort to comprehend the code.

\begin{figure}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
void doABC(){
	doA();
	doB("abc");
	doC();
}

void doDEF(){
  doA();
  doB("def");
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
void doABC(){
	do("abc");
}

void doDEF(){
	do(s, "def");
}

void doThis(String s){
  doA();
  doB(s);
  doC();
}
\end{javacode}}
\end{parcolumns}
\caption{Literal variability refactored.}
\label{fig:type2literal}
\end{figure}
